---
title: "MLBARCRT_generation"
author: "Xinwei Li\n li.xinwei@u.nus.edu"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
      highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

```


```{r, echo=FALSE, message=FALSE,results='hide'}
library(tictoc)
library(doParallel)
library(Rcpp)
library(RcppArmadillo)
library(RcppEigen)
library(RcppNumerical)
library(truncnorm)
#file_route = "D:\\onedrive\\OneDrive - National University of Singapore\\Desktop\\New folder\\MLBA_CRT\\RT_paper\\MLBA.cpp"

file_route = "D:\\onedrive\\OneDrive - National University of Singapore\\Desktop\\New folder\\MLBA_CRT\\RT_paper\\MLBA_H.cpp"
```
```{r}
sourceCpp(file_route)
```
# 1. Dataset Generation 


Set N = 200 independent observations. For each choice situation, there would  be nAttr = 3 attributes value,A,B, and C for each alternative, Alt1,Alt2, and Alt3, i.e. J = 3, with Response time ($RT_i, i =1,\cdots,N$). Choice,$RC_i$, would be made to prefer the one with larger probability with given RT and attributes value. 


## 1.1. Attribute value and response time random generation

Randomly generate attributes value for N situation, $A\sim N(3,4)$, $B\sim U[0,4]$,and $C\sim N(0,1)$. RT for each observation is decided by the $min_{i\in C_J}\{t_i = \frac{b_i-A}{v_i}\}$, where $v_i\sim N(d_i,1)$ and $b_i\sim CU(A,b)$. Denote X is the matrix of attributes' value, sorted in a long format, whose dimension is $(N J)\times nAttr$. $X = (X_1,X_2,\cdots,X_N)^T$, where $X_i=(X_{i1}^T,\cdots,X_{iJ}^T)^T, J$ is the number of alternatives.


```{r}
# dimension setting
N = 200
nAlt = 3
nAttr = 3

# attributes value generation
set.seed(2023) # seeds for training dataset

#set.seed(12) # seed for out-of-sample
A = rnorm(N*nAlt ,mean = 3, sd = 4)
B = runif(N*nAlt ,min = 0, max = 4)

C = rnorm(N*nAlt ,mean = 0, sd = 1)



X = cbind(A,B,C)

#X.df = scale(X, center =FALSE,scale = apply(X, 2, function(x){max(x)-min(x)}))
X.df = sapply(1:nAttr, function(i){(X[,i]-min(X[,i]))/(max(X[,i])-min(X[,i]))})
#X.df = X

head(X.df)
summary(X.df)
```

## 1.2. MLBA modelling

 Set the true value of MLBA parameters, following mainstream choice-RT MLBA structure (Trueblood et al., 2014)


| notion | parameter | value | status|
|--------|-------|-------|-------|
|Attribute Specific Parameters||||
|$\beta_A$|attribute A specific scaling parameter|1| will be estimated later|
|$\beta_B$|attribute B specific scaling parameter|2| will be estimated later|
|$\beta_C$|attribute C specific scaling parameter|5| will be estimated later|
|Alternative Specific Parameters||||
|$\zeta_1$|alternative specific constant with reference to alternative 2|0.3| will be estimated later|
|$\zeta_2$|alternative specific constant|-0.5| will be estimated later|
|$\zeta_3$|alternative specific constant|0|fixed|
|Process Parameters||||
|$\lambda_1$|gain attitude parameter for similarity|1 |  will be estimated later  |
|$\lambda_2$|loss attitude parameter for similarity|0.5 |  will be estimated later  |
|$b/A$| ratio of threshold over A|10| will be estimated later|
| $s_0$ |  noise standard deviation for drift rates  | 1| fixed |
|$A$|starting range|1|fixed|


```{r}
#true_param = list( lam1 = 1, lam2 = 0.5, zeta = c(0.3,-0.5,1), beta = c(1,2,5), s0 = 1, b_A = 10, A = 1)

true_param = list( lam1 = 1, lam2 = 0.5, zeta = c(0.3-1,-0.5-1,0), beta = c(1,2,5), s0 = 1, b_A = 10, A = 1,I0 = 1)
```


The MLBA assumes that evidence accumulates for each alternative j, agent i, independently and linearly, decided by starting point $k_{ij}\sim CU[0,A]$, drift rate $d_{ij} \sim TN(v_{ij},s_0)$, truncated below 0, and threshold $b$.


Moreover, the $v_{ij}$ is determined by the drift rate formula with the attribute value $X_{ij}$,a $nAttr\times 1$ matrix, and other parameters:

$$v_{ij} = \zeta_j+\sum_{m\in C_i}\sum_{k=1}^{nAttr} w_{i,mj,k}\beta_k (X_{ijk}-X_{imk}) \tag{1}$$

,where :

$$w_{i,mj,k} = exp\{-\lambda_1\beta_k(X_{ijk}-X_{imk})I(X_{ijk}-X_{imk}\ge 0)+\lambda_2\beta_k(X_{ijk}-X_{imk})I(X_{ijk}-X_{imk}<0)\}$$

According to the given parameter, the cumulative distribution function of alternative j for observation i,i.e. $RC_i =j$ taken response time $RT_i$ is:
$$\begin{aligned} F_{i}(j,RT) &= P\{\frac{CU[b-A,b]}{d_{ij}}\le RT\}\\
& = 1+\frac{b-A-d_{ij}RT}{A}\Phi(\frac{b-A-d_{ij}RT}{s_0RT})-\frac{b-d_{ij}RT}{A}\Phi(\frac{b-d_{ij}RT}{s_0RT})\\
& +\frac{s_0RT}{A}\phi(\frac{b-A-d_{ij}RT}{s_0RT})-\frac{s_0RT}{A}\phi(\frac{b-d_{ij}RT}{s_0RT})\end{aligned}\tag{2}$$

The density function is:
$$\begin{aligned} f_{i}(j,RT) &= \frac{1}{A}[ -d_{ij}\Phi(\frac{b-A-d_{ij}RT}{s_0RT})+d_{ij}\Phi(\frac{b-d_{ij}RT}{s_0RT})\\
& +s_0\phi(\frac{b-A-d_{ij}RT}{s_0RT})-s_0\phi(\frac{b-d_{ij}RT}{s_0RT})]\end{aligned}\tag{3}$$
, where $\Phi$ and $\phi$ are cdf and pdf for standard norm distribution.

Therefore, the probability to choose j when response time is RT for the observation i is:

$$MLBA_{pdf,i}(RC,RT|s_0,I_0,\lambda_1,\lambda_2,b,A) = f_{i}(RC,RT)\Pi_{j\in C_i,j\neq RC}[1-F_i(j,RT)]\tag{4}$$

<!-- the probability to choose j with given response time RT  for the observation i is: -->

<!-- $$MLBA_{cdf,i}(RC,RT|s_0,I_0,\lambda_1,\lambda_2,b,A) = \int_0^{RT}f_{i}(RC,t)\Pi_{j\in C_i,j\neq RC}[1-F_i(j,t)]dt\tag{5}$$ -->

For those observations whose response time is unknown, assume RT is large enough,
$$MLBA_{cdf,i}(RC|s_0,I_0,\lambda_1,\lambda_2,b,A) = \int_0^{\infty}f_{i}(RC,t)\Pi_{j\in C_i,j\neq RC}[1-F_i(j,t)]dt\tag{6}$$

## 1.2 RT and Choice generation
For each observation, the choice with least $t_i$ to arrive at the threshold is the chosen option and its response time is the observation's response time.

```{r}

tic("generation speed")
#set.seed(2024) # empirical
set.seed(23)
# decision-boundary draw
bi = runif(N, min = true_param$A*(true_param$b_A-1), max = true_param$A*true_param$b_A)
# decision rate mean
di = sapply(1:N, function(x){matrix(sapply(1:nAlt,function(c){RCPPdriftmean(X = X.df[((x-1)*nAlt+1):(x*nAlt),],beta = true_param$beta, zeta = true_param$zeta, lam1 = true_param$lam1, lam2 = true_param$lam2, choice = c,I0 = true_param$I0)}),ncol = 1)})

# decision rate draw (all is positive)
vi = apply(di, 2, function(x){rtruncnorm(1,a = 0,mean = x,sd = true_param$s0)})

# corresponding time
ti = bi/vi

# Response time generation
RT = apply(ti, 2, min)
# Response time generation
RC = apply(ti, 2, which.min)

summary(as.factor(RC))

summary(RT)
# generation dataset
# 1  2  3 
#59 45 96 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  1.884   4.613   5.720   7.360   8.457  50.784

# out-of-sample dataset
# 1  2  3 
#79 27 94 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  2.531   4.557   6.685   7.813   8.950  71.562 


# second out-of-sample dataset
#1  2  3 
#59 43 98 
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#  2.505   4.674   6.424   8.214   9.633  38.310 
```


```{r}
# real likelihood calculation

RCPPMLBA_Lik_CO(X = X.df,beta = true_param$beta, zeta = true_param$zeta,lam1 = true_param$lam1, lam2 = true_param$lam2, b = true_param$b_A*true_param$A, A = true_param$A, s = true_param$s0, choice = RC,I0 = true_param$I0)/N

RCPPMLBA_Lik_rtknown(X = X.df,beta = true_param$beta, zeta = true_param$zeta,lam1 = true_param$lam1, lam2 = true_param$lam2, b = true_param$b_A*true_param$A, A = true_param$A, s = true_param$s0, choice = RC, rt = RT,I0 = true_param$I0)/N

RCPPMLBA_Lik_rtg(X = X.df,beta = true_param$beta, zeta = true_param$zeta,lam1 = true_param$lam1, lam2 = true_param$lam2, b = true_param$b_A*true_param$A, A = true_param$A, s = true_param$s0, choice = RC, rt = RT,I0 = true_param$I0)/N


score_mlba_crt_all(X = X.df,beta = true_param$beta, zeta = true_param$zeta,lam1 = true_param$lam1, lam2 = true_param$lam2, b = true_param$b_A*true_param$A, A = true_param$A, s = true_param$s0, choice = RC, rt = RT)/N
score_mlba_rtg_all(X = X.df,beta = true_param$beta, zeta = true_param$zeta,lam1 = true_param$lam1, lam2 = true_param$lam2, b = true_param$b_A*true_param$A, A = true_param$A, s = true_param$s0, choice = RC, rt = RT)/N
score_mlba_co_all(X = X.df,beta = true_param$beta, zeta = true_param$zeta,lam1 = true_param$lam1, lam2 = true_param$lam2, b = true_param$b_A*true_param$A, A = true_param$A, s = true_param$s0, choice = RC)/N
```


```{r}
#wide format of dataframe
X_wide = matrix(t(X.df),ncol = 9, byrow = TRUE)
df = data.frame(RC,RT,X_wide)
colnames(df) = c("chosen","RT","A1","B1","C1","A2","B2","C2", "A3", "B3","C3")
head(df, 16)
```


```{r}
# export dataset
write.csv(df, "D:\\onedrive\\OneDrive - National University of Singapore\\Desktop\\New folder\\MLBA_CRT\\RT_paper\\MLBARCT_data_0501_hancock_test.csv", row.names=FALSE)
```



